Component response rate variation drives stability in large complex systems

### 2018-05-21 ms.Rmd
Minor tweaks

I have focused broadly on random complex systems, but

>>>>

I have focused broadly on random complex systems, but it is also worthwhile to consider more restricted interactions such as those of specific ecological networks[@Allesina]. These include systems in which all interactions (i.e., all off-diagonal elements of $M$) are negative (e.g., competitive networks), positive (e.g., mutualist networks), or $i$ and $j$ pairs have opposing signs (e.g., predator-prey networks). In general, competitive and mutualist networks tend to be stabilising, and predator-prey network tend to be stabilising[@Allesina2011]. When $Var(\gamma)$ is applied to each, the proportion of stable competitive and predator-prey networks increases, but the proportion of stable mutualist communities does not (see Supplementary Information). Additionally, when each component of $M$ is interpreted as a unique species and given a random intrinsic growth rate[@Dougoud2018], feasibility is not increased by $Var(\gamma)$, suggesting that variation in species generation time might be unlikely to drive stability in purely multi-species networks (see Supplementary Information).
